Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-10-26 papers/thesis-kirstie/thesis.tex
edits

Equations~\ref{eq:Fideal} and \ref{eq:Fexcess} show that the Helmholtz free energy 
\begin{equation}{F=F_{ideal} + F_{excess}}\end{equation} 
is a function of the number density n. For a spatially varying number density, 
as would be expected for a crystal, the free energy becomes a functional of 
the number density profile $n(\vec{r})$.  
\begin{equation}{F[n(\vec{r})]=F_{ideal}[n(\vec{r})] + F_{excess}[n(\vec{r})]}\end{equation} 
The functional for the ideal Helmholtz free energy is given by 
Equation~\ref{eq:Fideal-n(r)}, and the functional for the excess Helmholtz 
free energy depends on the particular fluid as defined by the spheres' 
interatomic potential V(r). To implement cDFT, the number density profile 
$n(\vec{r})$ is varied with the temperature fixed until the free energy 
is minimized. The minimum free energy and its corresponding number density 
profile are then the equilibrium values for that temperature.

@@

A simplified flowchart of the program created to investigate the freezing 
of a WCA fluid is shown on %pages x-x. 
The program takes four inputs: reduced number density n*, reduced temperature t*, 
a range of Gaussian 
widths gw, and a range of fraction of vacancies fv.The number density 
profile is varied by varying gw and fv, and the free energy $F[n(\vec{r})]$ 
is calculated for each profile until the minimum free energy is found for 
that combination of $n^*$ and $t^*$, which is known from cDFT to be unique. 
The process is then repeated to find the free energies at other number 
densities and temperatures.

\textbf{Program Implementation}

The program computes both the crystal and the homogeneous Helmholtz free 
energies. The Helmholtz free energy is minimized for a system with a fixed 
temperature, volume, and number density. The temperature, T is an input to 
the program. The number density, which is also an input to the program, 
is used to calculate the volume of one primitive cell over which the free 
energy is computed. The number of atoms in one primitive cell is one. To 
compute the free energy, it is necessary to compute both the ideal and 
excess free energies and add them, $F = F_{ideal} + F_{excess}$.
%\begin{displaymath}F_{homogeneous} = F_{ideal.homogeneous} + F_{excess.homogeneous}\end{displaymath}
%\begin{displaymath}F_{crystal} = F_{ideal.crystal} + F_{excess.crystal}\end{displaymath}
%\newline
%\newline\noindent Inputs: 
%t*, n*, range of gw values , range of fv values
%\newline Outputs: Homogeneous (liquid)  Helmholtz free energy (at the given T,V,N) 
%\newline\indent\indent\indent Crystal Helmholtz free energy (at the given T,V,N)

@@

%Compare:
\begin{displaymath}\text{If~~~~~~}\left(\frac{F}{N}\right)_{diff}<\text{~~~~Best}\left(\frac{F}{N}\right)_{diff}\end{displaymath}
\begin{displaymath}\text{Then~~~~~~}\text{Best}\left(\frac{F}{N}\right)_{diff}=\left(\frac{F}{N}\right)_{diff}\end{displaymath}
%\noindent Output:
\begin{displaymath}\text{Output:~~~~~~~~~~~~ Best}\left(\frac{F}{N}\right)_{crystal}\text{~~and~~~~~~}\left(\frac{F}{N}\right)_{homogeneous}\text{~~~~for the given T, n ~~~~~~~~~~~~~~~~~~~~~~~~~}\end{displaymath} 
%\begin{displaymath}\text{Best}\left(\frac{F}{N}\right)_{crystal}\end{displaymath}
%\begin{displaymath}\left(\frac{F}{N}\right)_{homogeneous}\end{displaymath}
%lattice_constant= pow(4*(1-fv)/reduced_density, 1.0/3)
\newline
\newline
*****   start stuff?  ******

@@

*****  end  stuff?  ******

@@

The excess Helmholtz free energy is particular to the fluid being modeled, 
as it depends on the interatomic potential V(r). 
%MOVE to METHODS start1 >>>
The WCA potential is not well suited for implementing Density Functional 
Theory.  Therefore, an erf potential which closely approximates the WCA 
potential at temperatures of interest will be used instead of the WCA 
potential. The erf potential is given by 
\begin{equation}
	{V_{erf}=-k_BT\ln\left[\frac{1}{2}\left(\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)+1\right)\right]}
\end{equation}

Unlike the WCA potential, the erf potential depends on temperature, but 
we temperature dependent parameters $\alpha(T)$ and $\Xi(T)$ to compensate for the
variance with temperature. The parameter $\alpha(T)$ is derived by setting 
the erf potential equal to the WCA potential when r equals $\alpha$ 
\begin{displaymath}{V_{erf}(r=\alpha)=V_{WCA}(r=\alpha)}\end{displaymath} 
and is given by 
\begin{equation}\label{alphaT}
	{\alpha(T)=\sigma\left(\frac{2}{1+\sqrt{\frac{k_BT}{\epsilon}\ln(2)}}\right)^\frac{1}{6}}
\end{equation} 
%%%%Unlike the WCA potential, the erf potential depends on temperature through the parameters $\alpha$ and $\Xi$. 
Figure \ref{fig:alphaXivsT} shows how 
$\alpha$ varies with temperature when $\sigma=1$ and $\epsilon=1$. 
% and Figure \ref{fig:erf_Potential} shows the erf potential at reduced 
%temperatures $\frac{k_BT}{\epsilon}=1$, $\frac{k_BT}{\epsilon}=2$, and 
%$\frac{k_BT}{\epsilon}=3$ alongside the WCA potential. 
%As seen in Figure \ref{fig:erf_potential}, the erf potentials closely 
%match the WCA potential for reduced temperatures below $\frac{k_BT}{\epsilon}=2$, 
%and for r/$\sigma$ less than ???. % so only values of $V_{erf}$ that are 
%much less than $k_BT$/$\epsilon$ ??? will be considered. 
% In these regions $\alpha$ decreases with increasing temperature, 
%and $\Xi$ increases with increasing temperature.
 %\begin{figure}[h!]
    %\centering
    %\begin{subfigure}[b]{0.4\linewidth}
      %\includegraphics[height=5cm]{plot_alpha.pdf}
      %\caption{$\alpha$ versus $k_BT/\epsilon$}
    %\end{subfigure} 
    %\begin{subfigure}[b]{0.4\linewidth}
      %\includegraphics[height=5cm]{plot_xi.pdf}
      %\caption{$\Xi$ versus $k_BT/\epsilon$}
    %\end{subfigure} 
    %\caption{These plots, generated with $\sigma=1$ and $\epsilon=1$, 
    %show how the parameters $\alpha$ and $\Xi$ vary with temperature. 
    %(a) $\alpha$ decreases with increasing temperature. (b) $\Xi$ rapidly 
    %increases for temperatures below $\frac{k_BT}{\epsilon}=52$ and then 
    %gradually decreases.}
    %\label{fig:alphaXivsT}
    %\end{figure}     
\begin{figure}[h!]
    \centering
    \includegraphics[height=9cm]{plot_alpha.pdf}
    \caption{Shows the temperature dependence of $\alpha$ vs $k_BT/{\epsilon}$ 
    for $\sigma=1$ and $\epsilon=1$}
    \label{fig:alphaXivsT}
  \end{figure}

To find values for $\Xi(T)$ we use the second virial 
coefficent $B_{2}$ from the equation of state expressed in terms of 
the virial expansion. 
\begin{equation}\label{virialequation}
    \frac{PV}{k_BT}=N\left(1+\frac{N}{V}B_2(T)+\left(\frac{N}{V}\right)^2B_3(T)+ \cdot\cdot\cdot\right) 
\end{equation}
where 
\begin{equation}
	B_{2}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}(r)}-1\right)d\vec{r} 
\end{equation}
The second virial coefficient can be derived from Euler's equation for 
the internal energy of a system, 
\begin{equation}U=TS-PV+\mu{N}\end{equation}
using the relations from statistical thermophysics which views the 
thermodynamic quantities as ensemble averages
\begin{equation}S=-k_B\sum_{i=0}^\infty{P_i\ln{P_i}}\end{equation}
\begin{equation}U=<E>=\sum_{i=0}^\infty{P_iE_i}\end{equation}
\begin{equation}N=<n>=\sum_{i=0}^\infty{P_in_i}\end{equation}
which, for a canonical ensemble, gives
\begin{equation}\frac{PV}{k_BT}=N + \beta\frac{\partial{F}_{excess}}{\partial{N}}{N} - \frac{F_{excess}}{k_BT}\end{equation}
Expressing the Helmholtz free energy in terms of the pair potential 
$V(r)$ results in the equation of state expressed in terms of the virial 
expansion as given by Equation~\ref{virialequation}.

The value of $\Xi$ at a given temperature, T, can be found computationally 
by equating the second virial coefficient evaluated for the error function 
potential $V_{erf}(r)$, and the second virial coefficent evalued for the 
WCA potential $V_{WCA}$.
\begin{equation}B_{2erf}(T) =B_{2WCA}(T)\end{equation}
Evaluating $B_{2}$ for the erf potential gives
\begin{equation}
	B_{2erf}(T) = \frac{\pi}{3}\Xi^3\left[\left(\frac{\alpha^3}{\Xi^3}+\frac{3\alpha}{2\Xi}\right)\left(1+\operatorname{erf}\left(\frac{\alpha}{\Xi}\right)\right)+\frac{1}{\sqrt{\pi}}\left(\frac{\alpha^2}{\Xi^2}+1\right)e^{-\left(\frac{\alpha}{\Xi}\right)^2}\right]
\end{equation}
where $\alpha(T)$ is given by Equation~\ref{alphaT} as before. Similarly, 
$B_{2WCA}$ can be found computationally from 
\begin{equation}
	B_{2WCA}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}_{WCA}(r)}-1\right)d\vec{r} 
\end{equation}
A plot of the resulting second virial coefficient $B_2(T)$  with respect 
to temperature is given in Figure~\ref{fig:B2vsT}, and a plot of $\Xi(T)$ obtained 
through this method is shown in Figure~\ref{fig:xi_fromB2vsT}. 
Figure~\ref{fig:erf_Potential_xifromB2} shows the erf potential generated with
$\alpha(T)$ and $\Xi(T)$ at a few different temperatures alongside the WCA 
potential which is not temperature dependent.

@@

%MOVE to METHODS end1 >>>

******  SFMT Functional ******

%MOVE to METHODS start2 >>>
In this paper,  $w_{2}(r)$ will be constructed using the following expresssion 
for $w_3(r)$ proposed by Schmidt\cite{schmidt2000fluid}.
\begin{equation}{w_3(r)=\frac{1}{2}}\left[1-\operatorname{erf}\left(\frac{r-\frac{\sigma}{2}}{\frac{\text{a}}{\sqrt{2}}}\right)\right]\end{equation} 
where $w_3(r)$ is subject to the boundary conditions $w_3(0)\approx{1}$ 
and $w_3(\infty)=0$. 
%\color{red}These boundary conditions are satisfied for $\Xi{\sqrt{2}<<\alpha}$, or $k_BT << 2.21$. \color{black} 
We replace Shcmidt's parameters $\sigma$ and $a$ with our temperature 
dependent parameters $\alpha(T)$ and $\Xi(T)$ which were defined above.
\begin{equation}\sigma = \alpha(T)\text{~~~~~~~and~~~~~~~} a = \Xi(T)\end{equation}
This gives the expression
\begin{equation}{w_3(r)=\frac{1}{2}}\left[1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)\right]\end{equation} 
Using Equation~\ref{w2_w3_relation}, shown again below, 
\begin{displaymath}{w_{3}=\int_{r}^{\infty}{w_{2}(\vec{r})dr}\mbox{~~~~or equivilantly,~~~~}-\frac{\partial{w_3(r)}}{\partial{r}}=w_2(r)}\end{displaymath}
and solving for $w_2(r)$
\begin{displaymath}{\frac{dw_3(r)}{dr}\bigg|_{\infty}-\frac{dw_3(r)}{dr}\bigg|_{r}=w_2(r)}\end{displaymath} 
we get \begin{equation}{ w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2} }\end{equation} %From the deconvolution equation \begin{equation}{-\frac{1}{2}f(r)=w_0*w_3 + w_1*w_2 -\vec{w}_{V1}*\vec{w}_{V2}}\end{equation} it follows that $w_2$ must satisfy the relation
Putting $w_2(r)$ into Equation~\ref{mayerder=w2convolution}, shown again below, 
\begin{displaymath}{\frac{df(r)}{dr}=\int_{-\infty}^{\infty}{w_2(r')w_2(r-r')dr'}}\end{displaymath}
gives
\begin{equation}{\frac{df(r)}{dr}=\frac{1}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\alpha}{\Xi}\right)^2}}\end{equation} 
which can be integrated to obtain the Mayer function
\begin{equation}{f(r)=\int_{\infty}^r{ \frac{1}{\Xi\sqrt{\pi}}e^{-\left(\frac{r'-\alpha}{\Xi}\right)^2}{dr'}}}\end{equation} 
The Mayer function for the error function potential $V_{erf}(r)$ is thus 
given by
\begin{equation}{f(r)=-\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)\right]}\end{equation} 
Combining this result with the definition of the Mayer function \begin{displaymath}f(r)=e^{-\frac{V(r)}{K_BT}}-1\end{displaymath} 
%This gives an interatomic potential of \begin{equation}{V_{erf}=-k_BT\ln(f(r)-1)}\end{equation} 
gives an expression for the for the error function potential  $V(r)=V_{erf}(r)$ 
\begin{equation}{V_{erf}(r)=-k_BT\ln\left[\frac{1}{2}\left(\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)+1\right)\right]}\end{equation} 
The two parameters $\alpha$ and $\Xi$ are given in equations (3) and (4), 
and are used to compensate for the temperature dependence that enters 
in through the expression for the error function potential $V_{erf}(r)$.
%determined to make $V_{erf}(r)$ match $V_{WCA}(r)$ as closely as 
%possible by compensating for the unwanted temperature dependence that shows 
%up in the error function potential $V_{erf}(r)$.
%MOVE to METHODS end2 >>>

**** FUNCTIONAL HERE! *****
\begin{align}
\Phi_1 &= -n_{0}ln(1-n_{3}) \\
\Phi_2 &= \frac{n_{1}n_{2}-\vec{n_{1}}\cdot\vec{n_{2}}}{1-n_{3}} \\
\Phi_3 &= \frac{{n_2}^3-3n_2\vec{n}_{v2}\cdot\vec{n}_{v2}+\frac{9}{2}[\vec{n}_{v2}\cdot{\overleftrightarrow{n}_{m2}}\cdot{\vec{n}_{v2}}-\operatorname{Tr}({\overleftrightarrow{n}^3_{m2}})]}{24\pi(1-n_3)^2}  
\end{align}

\begin{align}\label{eq:weights}
  w_{0}(r) &=\frac{w_{2}}{4\pi{r}^2} \\
  w_{1}(r) &=\frac{w_{2}}{4\pi{r}} \\
  w_2(r)&=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2}
  \\
  w_3(r)&=\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)\right]
\end{align}

Figure \ref{fig:weight_functions} shows a 1 dimensional view of the weight functions 
$w_0$, $w_1$, $w_2$, $w_3$ as they vary with distance along the z-axis. In three 
dimensions, the weighting functions $w_0$, $w_1$, $w_2$ are spherical shells 
centered at $\vec{r}$. As shown in the cross-sectional view in Figure \ref{fig:W0andW3}a, 
$w_2$ peaks at a radius of $|\vec{r}-\vec{r'}|=\frac{\alpha}{2}$, a width determined 
by $\frac{\Xi}{\sqrt{2}}$, and edges that tapers off on either side of the peak giving 
the shell. The weighting function $w_3$, shown in Figure \ref{fig:W0andW3}b is a solid 
sphere up to a radius of ?FIX? after which it tapers off over a distance of ?FIX?.

@@

 \begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{weight_functions.pdf}
    \caption{Shows how the weight functions $w_0$, $w_1$, $w_2$, $w_3$ vary along the 
    z-axis for a reduced temperature of 2}
    \label{fig:weight_functions}
  \end{figure}

 \begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\linewidth}
      \includegraphics[height=5cm]{W2.png}
      \caption{A crossectional view of $w_2$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.4\linewidth}
      \includegraphics[height=5cm]{W3.png}
      \caption{A crossectional view of $w_3$}
    \end{subfigure} 
    \caption{Cross-sectional views of the 3D weight functions. (a) $w_2$ is a 
    spherical shell in 3D with soft edges. Weight functions $w_0$ and $w_1$ 
    have a similar shape. (b) $w_3$ is a sphere with soft edges in 3D.}
    \label{fig:W0andW3}
    \end{figure}

@@

\section{Derivation of the Excess Free Energy from Scaled Particle Theory}
The excess chemical potential of a homogeneous fluid corresdponds to the 
reversible work of inserting a sphere of radius R 
into a fluid consisting of hard spheres of radius R. 
\begin{displaymath}\mu_{ex}=W_{rev}(R){~~~~}\text{work to insert a hard sphere of radius R}\end{displaymath}
This result is obtained by considering the difference in the excess Helmholtz 
free energy when one atom is added to the system. It was shown by Widom 
to be related to the ensemble average of the Boltzman factor for the 
potential energy difference $V_{diff}$ of a system with N atoms and one 
with N+1 atoms. The resulting equation is known as Widom's Insertion Formula.
%\begin{displaymath}\mu_{ex}=\frac{\partial{F_{ex}}}{\partial{N}}\bigg|_{T,V}{~~~~~~}\end{displaymath}
\begin{equation}\mu_{ex}=\frac{F_{ex}(N+1)-F_{ex}(N)}{\Delta{N}}\bigg|_{T,V}\end{equation}
\begin{equation}\label{widom}{~}=-k_BT\ln\left(<e^{-\beta{V_{diff}}}>\right)\end{equation}
%Equation~\ref{widom} is called Widom's Insertion Formula. 
\color{red}For a system... $<e^{-\beta{V_{diff}}}> \rightarrow e^{-\beta{V_{diff}}}$, and Equation~\ref{widom} becomes 
\begin{equation}\mu_{ex}=-k_BT\ln\left(e^{-\beta{V_{diff}}}\right)=-k_BT(-\beta{V}_{diff})=V_{diff}=W_{rev}\end{equation}\color{black}
%In a randomly positioned (I think it has to be homogeneous!)
\indent In a collection of hard spheres making up a hard sphere fluid, 
no energy would be required to place a hard sphere at points 
surrounded by an empty space the size of a hard sphere. But a hard sphere 
cannot be placed at points where a hard sphere would 
overlap another hard sphere; the energy required to do that would be infinite. 
Thus, for a Hard Sphere fluid, Equation~\ref{widom} becomes
\begin{equation}\mu_{ex}=-k_BT\ln\left(P_{NoOverlap}e^{-\beta{V}_{NoOverlap}}+P_{Overlap}e^{-\beta{V}_{Overlap}}\right)\end{equation}
\begin{equation}=-k_BT\ln\left(P_{NoOverlap}e^{-\beta{0}}+P_{Overlap}e^{-\beta\infty}\right)\end{equation}
\begin{equation}=-k_BT\ln\left(P_{NoOverlap}(1)+P_{Overlap}(0)\right)\end{equation}
\begin{equation}=-k_BT\ln\left(P_{NoOverlap}\right)\end{equation}
where $P_{NoOverlap}$ is the probablity of positions existing in the hard 
fluid that are surrounded by an empty space the size of a hard sphere.

>>>>

%Equations~\ref{eq:Fideal} and \ref{eq:Fexcess} show that the Helmholtz free energy 
%\begin{equation}{F=F_{ideal} + F_{excess}}\end{equation} 
%is a function of the number density n. For a spatially varying number density, 
%as would be expected for a crystal, the free energy becomes a functional of 
%the number density profile $n(\vec{r})$.

The functional for the ideal Helmholtz free energy is given by 
Equation~\ref{eq:Fideal-n(r)}, and the functional for the excess Helmholtz 
free energy depends on the particular fluid as defined by the spheres' 
interatomic potential V(r). To implement cDFT, the number density profile 
$n(\vec{r})$ is varied with the temperature fixed until the free energy 
is minimized. 
\begin{equation}{F[n(\vec{r})]=F_{ideal}[n(\vec{r})] + F_{excess}[n(\vec{r})]}\end{equation}
The minimum free energy and its corresponding number density 
profile are then the equilibrium values for that temperature.

@@

A simplified flowchart of the program created to investigate the freezing 
of a WCA fluid is shown below. The program takes four inputs: reduced number 
density n*, reduced temperature t*, a range of Gaussian 
widths gw, and a range of fraction of vacancies fv. The number density 
profile is varied by varying gw and fv, and the free energy $F[n(\vec{r})]$ 
is calculated for each profile until the minimum free energy is found for 
that combination of $n^*$ and $t^*$, which is known from cDFT to be unique. 
The process is then repeated to find the free energies at other number 
densities and temperatures.

%Program Implementation
The program computes both the crystal and the homogeneous Helmholtz free 
energies. The Helmholtz free energy is minimized for a system with a fixed 
temperature, volume, and number density. The temperature, T is an input to 
the program. The number density, which is also an input to the program, 
is used to calculate the volume of one primitive cell over which the free 
energy is computed. The number of atoms in one primitive cell is one. To 
compute the free energy, it is necessary to compute both the ideal and 
excess free energies and add them, $F = F_{ideal} + F_{excess}$.
%\begin{displaymath}F_{homogeneous} = F_{ideal.homogeneous} + F_{excess.homogeneous}\end{displaymath}
%\begin{displaymath}F_{crystal} = F_{ideal.crystal} + F_{excess.crystal}\end{displaymath}
%\newline
%\newline\noindent Inputs: 
%t*, n*, range of gw values , range of fv values
%\newline Outputs: Homogeneous (liquid)  Helmholtz free energy (at the given T,V,N) 
%\newline\indent\indent\indent Crystal Helmholtz free energy (at the given T,V,N)

@@

%Compare:
\begin{displaymath}\text{If~~~~~~}\left(\frac{F}{N}\right)_{diff}<\text{~~~~Best}\left(\frac{F}{N}\right)_{diff}\end{displaymath}
\begin{displaymath}\text{Then~~~~~~}\text{Best}\left(\frac{F}{N}\right)_{diff}=\left(\frac{F}{N}\right)_{diff}\end{displaymath}
%\noindent Output:
\begin{displaymath}\text{Output:~~~~~~~~~~~~ Best}\left(\frac{F}{N}\right)_{crystal}\text{~~and~~~~~~}\left(\frac{F}{N}\right)_{homogeneous}\text{~~~~for the given T, n ~~~~~~~~~~~~~~~~~~~~~~~~~}\end{displaymath} 
%\begin{displaymath}\text{Best}\left(\frac{F}{N}\right)_{crystal}\end{displaymath}
%\begin{displaymath}\left(\frac{F}{N}\right)_{homogeneous}\end{displaymath}
%lattice_constant= pow(4*(1-fv)/reduced_density, 1.0/3)
\newline
\newline
*****   start stuff  ******

@@

*****  end  stuff  ******

@@

%The excess Helmholtz free energy is particular to the fluid being modeled, 
%as it depends on the interatomic potential V(r). 
We use Soft Fundamental Measure Theory to find the excess Helmholtz free energy.
The functional is written in general form as 
\begin{displaymath}{F_{excess}[n(\vec{r})]= k_BT\int(\Phi_1(\vec{r})+\Phi_2(\vec{r})+\Phi_3(\vec{r}{)) d}\vec{r}}\end{displaymath} 
where
\begin{align}
\Phi_1 &= -n_{0}ln(1-n_{3}) \\
\Phi_2 &= \frac{n_{1}n_{2}-\vec{n_{1}}\cdot\vec{n_{2}}}{1-n_{3}} \\
\Phi_3 &= \frac{{n_2}^3-3n_2\vec{n}_{v2}\cdot\vec{n}_{v2}+\frac{9}{2}[\vec{n}_{v2}\cdot{\overleftrightarrow{n}_{m2}}\cdot{\vec{n}_{v2}}-\operatorname{Tr}({\overleftrightarrow{n}^3_{m2}})]}{24\pi(1-n_3)^2}  
\end{align} 
and Tarazona's tensor expression~\cite{tarazonaphi3, santos2012phi3} is used 
for $\Phi_3$. The weigthed densities $n_0, n_1, n_2,$ and $n_3$ are found from
\begin{equation}{n_i(\vec{r})=\int_{Volume}{n(\vec{r'})w_i(|\vec{r}-\vec{r'}|)d{\vec{r'}}}}\end{equation}
where the weight functions $w_0, w_1, w_2,$ and $w_3$ are given by
\begin{align}\label{eq:weights}
  w_{0}(r) &=\frac{w_{2}}{4\pi{r}^2} \\
  w_{1}(r) &=\frac{w_{2}}{4\pi{r}} \\
  w_2(r)&=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2}
  \\
  w_3(r)&=\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)\right]
\end{align}
The weight fucntions $w_{2}(r)$ and $w_{3}(r)$ are constructed using 
Schmidt's proposed erf model~\cite{schmidt2000fluid} in which he set
\begin{equation}{w_3(r)=\frac{1}{2}}\left[1-\operatorname{erf}\left(\frac{r-\frac{\sigma}{2}}{\frac{\text{a}}{\sqrt{2}}}\right)\right]\end{equation} 
where $w_3(r)$ is subject to the boundary conditions $w_3(0)\approx{1}$ 
and $w_3(\infty)=0$. 
%\color{red}These boundary conditions are satisfied for $\Xi{\sqrt{2}<<\alpha}$, or $k_BT << 2.21$. \color{black} 
Our functional is  created by replacing Schmidt's parameters $\sigma$ 
and $a$ with our temperature dependent parameters $\alpha(T)$ and $\Xi(T)$.
\begin{equation}\sigma = \alpha(T)\text{~~~~~~~and~~~~~~~} a = \Xi(T)\end{equation}

The two parameters $\alpha$ and $\Xi$ are used to compensate for the 
temperature dependence that enters in through the expression for the 
error function potential $V_{erf}(r)$ which is used to approximate the
non-temperature dependent WCA potential that is more difficult to 
implement computationally. The erf potential emerges from the relationships
that the weight functions must satisfy.
%potential at temperatures of interest will be used instead of the WCA potential. 
Using Equation~\ref{w2_w3_relation}, shown again below, 
\begin{displaymath}{w_{3}=\int_{r}^{\infty}{w_{2}(\vec{r})dr}\mbox{~~~~or equivilantly,~~~~}-\frac{\partial{w_3(r)}}{\partial{r}}=w_2(r)}\end{displaymath}
and solving for $w_2(r)$
\begin{displaymath}{\frac{dw_3(r)}{dr}\bigg|_{\infty}-\frac{dw_3(r)}{dr}\bigg|_{r}=w_2(r)}\end{displaymath} 
we get \begin{equation}{ w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2} }\end{equation} %From the deconvolution equation \begin{equation}{-\frac{1}{2}f(r)=w_0*w_3 + w_1*w_2 -\vec{w}_{V1}*\vec{w}_{V2}}\end{equation} it follows that $w_2$ must satisfy the relation
Putting $w_2(r)$ into Equation~\ref{mayerder=w2convolution}, shown again below, 
\begin{displaymath}{\frac{df(r)}{dr}=\int_{-\infty}^{\infty}{w_2(r')w_2(r-r')dr'}}\end{displaymath}
gives
\begin{equation}{\frac{df(r)}{dr}=\frac{1}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\alpha}{\Xi}\right)^2}}\end{equation} 
which can be integrated to obtain the Mayer function
\begin{equation}{f(r)=\int_{\infty}^r{ \frac{1}{\Xi\sqrt{\pi}}e^{-\left(\frac{r'-\alpha}{\Xi}\right)^2}{dr'}}}\end{equation} 
The Mayer function for the error function potential $V_{erf}(r)$ is thus 
given by
\begin{equation}{f(r)=-\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)\right]}\end{equation} 
Combining this result with the definition of the Mayer function \begin{displaymath}f(r)=e^{-\frac{V(r)}{K_BT}}-1\end{displaymath} 
%This gives an interatomic potential of \begin{equation}{V_{erf}=-k_BT\ln(f(r)-1)}\end{equation} 
gives an expression for the for the error function potential  $V(r)=V_{erf}(r)$ 
\begin{equation}
	V_{erf}(r)=-k_BT\ln\left[\frac{1}{2}\left(\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)+1\right)\right]
\end{equation}

Expressions for $\alpha(T)$ and $\Xi(T)$  can be found as follows. 
The parameter $\alpha(T)$ is derived by setting 
the erf potential equal to the WCA potential when r equals $\alpha$ 
\begin{equation}{V_{erf}(r=\alpha)=V_{WCA}(r=\alpha)}\end{equation} 
and is given by 
\begin{equation}\label{alphaT}
	{\alpha(T)=\sigma\left(\frac{2}{1+\sqrt{\frac{k_BT}{\epsilon}\ln(2)}}\right)^\frac{1}{6}}
\end{equation} 
Figure \ref{fig:alphaXivsT} shows how $\alpha$ varies with temperature 
when $\sigma=1$ and $\epsilon=1$.    
\begin{figure}[h!]
    \centering
    \includegraphics[height=9cm]{plot_alpha.pdf}
    \caption{Shows the temperature dependence of $\alpha$ vs $k_BT/{\epsilon}$ 
    for $\sigma=1$ and $\epsilon=1$}
    \label{fig:alphaXivsT}
  \end{figure}
The value of $\Xi$ at a given temperature, T, can be found computationally 
by equating the second virial coefficient evaluated for the error function 
potential $V_{erf}(r)$, and the second virial coefficent evalued for the 
WCA potential $V_{WCA}$.
\begin{equation}B_{2erf}(T) =B_{2WCA}(T)\end{equation}
The second virial coefficient can be derived from Euler's equation for 
the internal energy of a system, 
\begin{equation}U=TS-PV+\mu{N}\end{equation}
using the relations from statistical thermophysics which views the 
thermodynamic quantities as ensemble averages
\begin{equation}S=-k_B\sum_{i=0}^\infty{P_i\ln{P_i}}\end{equation}
\begin{equation}U=<E>=\sum_{i=0}^\infty{P_iE_i}\end{equation}
\begin{equation}N=<n>=\sum_{i=0}^\infty{P_in_i}\end{equation}
which, for a canonical ensemble, gives
\begin{equation}\frac{PV}{k_BT}=N + \beta\frac{\partial{F}_{excess}}{\partial{N}}{N} - \frac{F_{excess}}{k_BT}\end{equation}
Expressing the Helmholtz free energy in terms of the pair potential 
$V(r)$ results in an equation of state expressed in terms of the virial expansion 
\begin{equation}\label{virialequation}
    \frac{PV}{k_BT}=N\left(1+\frac{N}{V}B_2(T)+\left(\frac{N}{V}\right)^2B_3(T)+ \cdot\cdot\cdot\right) 
\end{equation}
where 
\begin{equation}
	B_{2}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}(r)}-1\right)d\vec{r} 
\end{equation}
Evaluating $B_{2}$ for the erf potential gives
\begin{equation}
	B_{2erf}(T) = \frac{\pi}{3}\Xi^3\left[\left(\frac{\alpha^3}{\Xi^3}+\frac{3\alpha}{2\Xi}\right)\left(1+\operatorname{erf}\left(\frac{\alpha}{\Xi}\right)\right)+\frac{1}{\sqrt{\pi}}\left(\frac{\alpha^2}{\Xi^2}+1\right)e^{-\left(\frac{\alpha}{\Xi}\right)^2}\right]
\end{equation}
where $\alpha(T)$ is given by Equation~\ref{alphaT}. Similarly, 
$B_{2WCA}$ can be found computationally from 
\begin{equation}
	B_{2WCA}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}_{WCA}(r)}-1\right)d\vec{r} 
\end{equation}

A plot of the resulting second virial coefficient $B_2(T)$  with respect 
to temperature is given in Figure~\ref{fig:B2vsT}, and a plot of $\Xi(T)$ obtained 
through this method is shown in Figure~\ref{fig:xi_fromB2vsT}. 
Figure~\ref{fig:erf_Potential_xifromB2} shows the erf potential generated with
$\alpha(T)$ and $\Xi(T)$ at a few different temperatures alongside the WCA 
potential which is not temperature dependent.

@@

\color{red}
Figure \ref{fig:weight_functions} shows a 1 dimensional view of the weight functions 
$w_0$, $w_1$, $w_2$, $w_3$ as they vary with distance along the z-axis. In three 
dimensions, the weighting functions $w_0$, $w_1$, $w_2$ are spherical shells 
centered at $\vec{r}$. As shown in the cross-sectional view in Figure \ref{fig:W0andW3}a, 
$w_2$ peaks at a radius of $|\vec{r}-\vec{r'}|=\frac{\alpha}{2}$, a width determined 
by $\frac{\Xi}{\sqrt{2}}$, and edges that tapers off on either side of the peak giving 
the shell. The weighting function $w_3$, shown in Figure \ref{fig:W0andW3}b is a solid 
sphere up to a radius of ?FIX? after which it tapers off over a distance of ?FIX?.

@@

 \begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{weight_functions.pdf}
    \caption{\color{red}RERUN for NEW XI!\color{black}Shows how the weight functions $w_0$, $w_1$, $w_2$, $w_3$ vary along the 
    z-axis for a reduced temperature of 2}
    \label{fig:weight_functions}
  \end{figure}

 \begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\linewidth}
      \includegraphics[height=5cm]{W2.png}
      \caption{A crossectional view of $w_2$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.4\linewidth}
      \includegraphics[height=5cm]{W3.png}
      \caption{A crossectional view of $w_3$}
    \end{subfigure} 
    \caption{\color{red}RERUN for NEW XI!\color{black}Cross-sectional views of the 3D weight functions. (a) $w_2$ is a 
    spherical shell in 3D with soft edges. Weight functions $w_0$ and $w_1$ 
    have a similar shape. (b) $w_3$ is a sphere with soft edges in 3D.}
    \label{fig:W0andW3}
    \end{figure} 
\color{black}

@@
